%-------------------------
% Resume in Latex
% Author : Kyle Hovey
% Template Creator : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://kylehovey.github.io}{\Large Kyle Hovey}} & Email : \href{mailto:khoveyc@gmail.com}{khoveyc@gmail.com}\\
	\href{http://kylehovey.github.io}{kylehovey.github.io} & Mobile : +1-209-768-7550 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Utah State University}{Logan, UT}
      {Computational Mathematics Major;  GPA:  3.87}{Aug. 2015 -- Current}
    \resumeSubheading
      {Cuesta College}{San Luis Obispo, CA}
      {Three semesters to transfer;  GPA: 3.95}{Jan. 2014 -- May. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {USU Power Electronics Laboratory}{Logan, UT}
      {Software Engineer / Research Assistant}{Jan 2016 - Present}
      \resumeItemListStart
        \resumeItem{CAN Data Graphing Utility}
        {As a part of the AMPED project (geared towards extending battery life with smarter cycling) we accrued Terabytes of sensor data that needed to be visualized. I created a HTML5 asynchronous web-app for generating and sharing graphs of this data.}
      \resumeItem{Square One - Altium Library Management System}
        {I created a system for mass-submitting tickets for new parts to be added to our in-house Altium Database and verified by librarians. This system integrates with OctoPart and support auto-filling of data and will support BOM upload and automated price-minimizing order-form generation.}
      \resumeItem{Graphic Design}
      {I designed all the banners and window decals around our facilities in Logan, UT. In the process, I utilized a unified color palette for all the facets of our organization.}
      \resumeItem{Web Development}
        {I created the first revision of the SELECT website, which utilized a responsive single-page design and aesthetic harmony of data presented therein. The current website is not my doing, however.}
      \resumeItemListEnd

    \resumeSubheading
      {USU GASLab}{Logan, UT}
      {Software Engineer}{Apr 2017 - Present}
      \resumeItemListStart
      \resumeItem{Cubium Software Project}
      {I am in the software team of the Get-Away-Special small-satellite program at Utah State University. We continue to develop open source subscription-based plug and play software for small satellite application as well as develop new hardware that will empower individuals to deploy experiments on a budget.}
      \resumeItemListEnd

    \resumeSubheading
      {West Coast Astronomical Society}{Santa Margarita, CA}
      {Head of Mechatronics}{Jun 2014 - Jan 2015}
      \resumeItemListStart
        \resumeItem{Telescope Automation}
        {I was in charge of automating the hardware of a Meade 10`` telescope with the intention of streamlining the process of speckle interferometry to more accurately detect the positions of binary star systems. I implemented new affordable tech that will enable more people to observe countless binary+ star systems.}
      \resumeItemListEnd

    \resumeSubheading
      {Cuesta College}{San Luis Obispo, CA}
      {Tutor}{Aug. 2014 -- May. 2015}
      \resumeItemListStart
      \resumeItem{Math / Physics Tutor}
        {At Cuesta College I tutored all levels of mathematics and frequently had teachers send students to me so that I could explain new concepts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{USU Hackathon - 1st Place}
    {I took first place at the Utah State University intercollegiate hackathon for my solo development work on a procedurally generated terrain-based music visualizer entitled ``Acoustic Forest``.}
    \resumeSubItem{USU - Deans List}
    {I am a current member of the Dean's List at Utah State University.}
    \resumeSubItem{Cuesta College - FBSA}
    {I was awarded the Frank Brown Science Award for outstanding academic achievement.}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{8 Bit Spaghetti}
      {8-bit processor that I designed and built using TTL. I have now helped many students around the world build versions of my design.}
    \resumeSubItem{Dream Cloak LED Display}
    {In five days I designed and built a 15x30 24-bit wearable RGB LED display and a web app to control it wirelessly.}
    \resumeSubItem{Euler Golf}
      {HTML5 game based on a problem I conceived involving recursive movement over the Gaussian Integers.}
    \resumeSubItem{CALSim}
      {In-browser WireWorld cellular automaton interpreter with built in key-commands.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
        \textbf{Languages}{: JS, C++, Python, Bash, Java, PHP, LaTeX}
      \hfill
      \textbf{Technologies}{: jQuery, lodash, Node.js, Vim}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
